Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-03-05 resex.tex
Revised results section on 10th-turn pulsing.

\begin{figure*}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_intensity.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_emit2_rel.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_emit1.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_emit2.png}
	\end{minipage}	
	\caption{\label{fig:10thsim} Relative intensity (top left) and relative vert. emittance (top right), and hor. (bottom left) and vert. (bottom right) emittance obtained from simulations (distribution tracking) based on the 2016 injection optics with standard errors and $(Q_x,Q_y)=(64.28,59.31)$. The solid line indicates an excitation with only $10^{\mathrm{th}}$~turn pulsing in V and the dotted line with $10^{\mathrm{th}}$~turn pulsing in V plus a random dipole noise component in H+V of 6~nrad.}
\end{figure*}

\begin{figure}
		\centering
%		\includegraphics[width=0.8\linewidth]{2016_scale_amp_10v_ran_lbllong_sim.png}
\includegraphics[width=1.0\linewidth]{2016_scale_amp_10v_ran_lblshort_sim_prstab.png}
	\caption{\label{fig:10thexploss} Comparison of scaling of loss rates $R$ as defined in Eqn.~\ref{eqn:lossrate} with the excitation amplitude for $10^{\mathrm{th}}$~turn pulsing in~V. The experimental results for a maximum excitation of $A_{\mathrm{max}}=48$~nrad are shown in black and for $A_{\mathrm{max}}=96$~nrad in green. The excitation amplitude error is 50\% and the error on the loss rate is the pure statistical error on the mean. The simulation results (see Fig.~\ref{fig:10thsim}) for 2016 injection optics, standard errors, $(Q_x,Q_y)=(64.28,59.31)$, $10^{\mathrm{th}}$~turn pulsing in V plus random dipole noise in H+V of 6~nrad are shown in red together with their statistical error. The loss rates follow approximately a quadratic behavior illustrated by a second order polynomial fit to the data shown as solid (for bunches with transverse damper off) or dashed (for bunches with transverse damper on) line.}
\end{figure}

>>>>

\begin{figure*}
  \begin{tabular}{cc}
    \includegraphics[width=0.49\textwidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_intensity.png} &
    \includegraphics[width=0.49\textwidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_emit2_rel.png} \\
    \includegraphics[width=0.49\textwidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_emit1.png} &
    \includegraphics[width=0.49\textwidth]{2016injerra2b2uran1_2e-3_10thV_3_5um_emit2.png} \\
  \end{tabular}	
  \caption{Simulations (with the distribution-tracking method) based
    on the 2016 injection optics with standard lattice errors and
    tunes $(Q_x, Q_y) = (64.28, 59.31)$: relative beam intensity (top
    left); normalized horizontal (bottom left) and vertical (bottom
    right) emittances; vertical emittance relative to its initial
    value (top right). The solid lines indicate the effect of
    $10^{\mathrm{th}}$~turn pulsing in the vertical plane. The dotted
    lines include both the resonant excitation and a random dipole
    noise component of 6~nrad (in both horizontal and vertical
    planes).}
  \label{fig:10thsim}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{2016_scale_amp_10v_ran_lblshort_sim_prstab.png}
  \caption{Comparison between experiments and simulations of loss
    rates vs.\ resonant excitation amplitude for
    $10^{\mathrm{th}}$~turn pulsing in the vertical plane. The
    relative average loss rate~$R$ is defined in
    Eq.~\ref{eqn:lossrate}. The experimental results for a maximum
    excitation amplitude of 48~nrad are shown in black and those for
    96~nrad are plotted in green (see also Fig.~\ref{fig:10thexp},
    left, for instance). The results with damper off are represented
    by solid dots, those with damper on are shown with open
    circles. The simulation results, including random dipole noise,
    are shown in red (see also Fig.~\ref{fig:10thsim}). Statistical
    and systematic uncertainties are discussed in the text. The curves
    represent empirical quadratic fits to the data with damper off
    (solid) and with damper on (dashed).}
  \label{fig:10thexploss}
\end{figure}
